\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{
 a4paper,
 total={170mm,257mm},left=20mm,top=10mm}

\begin{document}

\section{Audience}

\begin{itemize}
  \item With this system, users can easily make money         transactions.
  \item In addition, through this system, anyone can bring their money from a Direct card to the account.
  \item Also, here, we have used a medium through which users can easily add their money at any time.
  \item Users can easily pay their bills, such as electricity, water, gas, they can pay any bill. In addition, the admin can add any user if they have any outstanding bills.
  \item Users can easily donate anywhere. Here they can pay even if they hide their identities.
  \item Users will be able to withdraw money at any time and will be able to withdraw cash very carefully. Here the user's identity is verified in different ways so that the money does not reach the rogue user.
  \item The student will be able to open an account in our banking system. No problem. We don't need any passport or sleep card to open an account here.
  \item Student are also transfer any cash without any problem.
\end{itemize}


\section{Motivation}
\begin{itemize}
\item Today our world is in tune with modernity and if we want to keep pace with this we have to be with it. Now we have this digital system so that people can carry their money without any worries.
\item We have taken this kind of project because many people open bank accounts without understanding much. They face a lot of difficulties with money, so they often give money to another account.
\item In addition, it is taken by us so that any user can use this application very easily.
\item A unique advantage here is that those who want to work with digital money have done it very nicely in this project. As a result, they can easily buy this money with money. And they can easily see the value of it.
\item We are adding another feature here that allows users to easily add money from their digital wallets, such as bKash, Cash, Way, Rocket, and MasterCard, which is not the case with many banks.
\item Apart from this, students in our country cannot open an account without their NID cards. As a result, they cannot accumulate their savings. But in our banking service, a student can open an account with their ID card. And he can accept all kinds of services.
\item Many banks charge a fee to pay any bill, but we do not capture any charges in this system. They can exchange money completely free of charge.

\end{itemize}

\end{document}